Amazonian Narratives in Presidential Discourse (1985 to 2020)

### 2021-11-06 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#updated dictionary #cleaned stop words #removed redundant tables

# Remove stop words and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil", "companheiro", "senhores",
                                          "companheiras", "companheiros", "companheira",
                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite site",
                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "bahia", "é",
                                          "lá", "et", "in"))

@@

# Let's get the gamma (percent of topic in document for speakers)
amazon_lda_presid <- tidy(amazon_lda, matrix = "gamma") %>%
  arrange(desc(gamma)) %>%
  group_by(document) %>%
  filter(row_number() %in% 1:2) %>% # get the top 3 topics per speaker
  arrange(document) %>%
  mutate(gamma = round(gamma, 3)) %>%
  distinct() %>% 
  rename (president = document) %>% 
  kableExtra::kbl(caption = "Top 2 Topics Per Speaker") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
amazon_lda_presid # Only Collor associated with topic cluster that mentions "ambiente"...
```

@@

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas") # This appears harder to operationalize than others...

@@

# Visualize correlations
am_narratives <- Amazon_speeches %>%
  select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, name) %>% 
  summarise(value = sum(value)) %>% 
  rename(narrative = name)
ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")

# Narrative per president, frequency table
pres_narratives <- Amazon_speeches %>%
  select(-c(context, text, fulltext, year, party, date, title, doc_id, location)) %>%
  group_by(president) %>%
  summarise(across(everything(), sum))
kableExtra::kbl(pres_narratives, caption = "Narratives per President in Brazil") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")

>>>>

# Remove stop words and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil", "companheiro", "senhores",
                                          "companheiras", "companheiros", "companheira",
                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul",
                                          "norte", "mato grosso","outro", "onde", "discurso", "parte", "anos", "cada", "todo", 
                                          "porto velho", "visite site", "site secretaria", "minas gerais", "lula silva", 
                                          "inácio lula", "amapa", "bahia", "é", "lá", "et", "in", "httpwww"))

@@

# Let's get the gamma (percent of topic in document for speakers)
amazon_lda_presid <- tidy(amazon_lda, matrix = "gamma") %>%
  arrange(desc(gamma)) %>%
  group_by(document) %>%
  filter(row_number() %in% 1:2) %>% # get the top 2 topics per speaker
  arrange(document) %>%
  mutate(gamma = round(gamma, 3)) %>%
  distinct() %>% 
  rename (president = document) %>% 
  kableExtra::kbl(caption = "Top 2 Topics Per Speaker") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
amazon_lda_presid # Only Collor associated with topic cluster that mentions "ambiente"...
```

@@

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto|madeireira|produzir")
conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|protecao|proteger")
anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas|ong|xiita") # This appears harder to operationalize than others...

@@

# Visualize correlations
am_narratives <- Amazon_speeches %>%
  select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, name) %>% 
  summarise(value = sum(value)) %>% 
  rename(narrative = name)
ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
    facet_wrap(~narrative)
